{\bf {\Large Four decades of water quality change in the upper San Francisco Estuary}}

### 2017-10-19 sftrends_manu.Rnw
med chl in table 1

locs <- delt_dat %>% 
  select(Location, Site_Code, Latitude, Longitude, nh, no23, din) %>% 
  gather('var', 'val', nh:din) %>% 
  group_by(Location, Site_Code, Latitude, Longitude, var) %>% 
  summarise(
    len = length(na.omit(val)),
    val = mean(val, na.rm = TRUE), 
    val = round(val, 2)
  ) %>% 
  ungroup %>% 
  gather('sum', 'val', val:len) %>% 
  unite('varsum', var, sum) %>% 
  spread(varsum, val) %>% 
  mutate(
    Location = factor(Location, 
                      levels = c('Delta', 'Middle', 'Suisun'), 
                      labels = c('Peripheral', 'Interior', 'Suisun')
                      ), 
    Site_Code = factor(Site_Code, 
                       levels = rev(c('D7', 'D6', 'D4', 'D28', 'D26', 'D19', 'P8', 'MD10', 'C10', 'C3'))
                       ), 
    Latitude = round(Latitude, 2),
    Longitude = round(Longitude, 2)
  ) %>% 
  arrange(Location, Site_Code)

# table stuff
cap.val <- 'Monitoring stations in the upper San Francico Estuary used to evaluate nitrogen trends. Records from 1976 to 2013 were evaluated using the total observations ($n$) at each station. Average units of nitrogen are reported in mg L$^{-1}$.'
cgrps <- c('', '', 'DIN', 'NH$_{4}^{+}$', 'NO$_{2}^{-}$/NO$_{3}^{2-}$')
rgrps <- locs$Location %>% unique
stats <- locs$Site_Code
totab <- locs[, -c(1, 2)]
names(totab) <- c('Lat', 'Lon', '$n$', 'Ave.', '$n$', 'Ave.','$n$', 'Ave.')

>>>>

locs <- delt_dat %>% 
  select(Location, Site_Code, Latitude, Longitude, nh, no23, din) %>% 
  gather('var', 'val', nh:din) %>% 
  group_by(Location, Site_Code, Latitude, Longitude, var) %>% 
  summarise(
    len = length(na.omit(val)),
    val = median(val, na.rm = TRUE), 
    val = round(val, 2)
  ) %>% 
  ungroup %>% 
  gather('sum', 'val', val:len) %>% 
  unite('varsum', var, sum) %>% 
  spread(varsum, val) %>% 
  mutate(
    Location = factor(Location, 
                      levels = c('Delta', 'Middle', 'Suisun'), 
                      labels = c('Peripheral', 'Interior', 'Suisun')
                      ), 
    Site_Code = factor(Site_Code, 
                       levels = rev(c('D7', 'D6', 'D4', 'D28', 'D26', 'D19', 'P8', 'MD10', 'C10', 'C3'))
                       ), 
    Latitude = round(Latitude, 2),
    Longitude = round(Longitude, 2)
  ) %>% 
  arrange(Location, Site_Code)

# table stuff
cap.val <- 'Monitoring stations in the upper San Francico Estuary used to evaluate nitrogen trends. Records from 1976 to 2013 were evaluated using the total observations ($n$) at each station. Median values are reported in mg L$^{-1}$.'
cgrps <- c('', '', 'DIN', 'NH$_{4}^{+}$', 'NO$_{2}^{-}$/NO$_{3}^{2-}$')
rgrps <- locs$Location %>% unique
stats <- locs$Site_Code
totab <- locs[, -c(1, 2)]
names(totab) <- c('Lat', 'Lon', rep(c('$n$', 'Med.'), 3))
